All Your Graphs Belong to Us

### 2012-07-15 doc/asplos13/implementation.tex
added scheduling description

Grappa's scheduler is simple. When

@@

>>>>

Each core in the Grappa system has its own independent scheduler. Each
scheduler has three main tasks to perform.  First, it must ensure that
its communication resources are serviced reasonably often. Second, it
must ensure that if a running task was waiting on a long-latency
operation and that operation has completed, the task will be
rescheduled. Third, if there are tasks waiting to be run and spare
execution resources, the tasks must be matched with idle workers.

Each scheduler has three queues:
\begin{description}
\item{Ready worker queue} This is a FIFO queue of tasks that are
  matched with workers and are ready to execute.
\item{Private task queue} This is a FIFO queue of tasks that must run on this core.
\item{Public task queue} This is a LIFO queue of tasks that are
  waiting to be matched with workers. Tasks may be stolen from this
  queue by other cores in the system; this is described in the next section.
\end{description}

Whenever a task yields or suspends, the scheduler makes a decision
about what to do next. First, it determines if it is time to service
the communication resources should be serviced. This is done on a
periodic basis. Second, it determines if any workers with running
tasks are ready to execute; if so, one is scheduled. Finally, if there
are no workers ready to run, but there are tasks waiting to be matched
with workers, an idle worker is woken (or a new worker is spawned),
matched with a task, and scheduled.

The scheduler uses its core's timestamp counter to track time. The
timestamp counter is read once per scheduling decision. Timestamp
values are not shared between cores. We use timestamp values only to
ensure period execution of communication maintenance tasks; being
wrong will only change the rate of these events with a potential
performance cost, and no correctness violation. Nevertheless, we
assume Grappa will run on machines with modern timestamp counter
implementations that are monotonic and frequency-compensated.

@@

\TODO{BrandonM or Jacob}
